---
title: "iteration"
author: "Nelson Gaillard"
date: "2025-11-13"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

set.seed(1)
```

## Do something simple

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```

I want a function to compute z-scores

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}

z_scores(x_vec)
```

Try my function on some other things. These should give errors.

```{r, error = TRUE}
z_scores(3)
z_scores("my name is jeff")
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
```

## Multiple outputs

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```

Check that the function works.

```{r}
x_vec = rnorm(100, mean = 3, sd = 4)
mean_and_sd(x_vec)
```

## Multiple inputs

I'd like to do this with a function.

```{r}
sim_data = 
  tibble(
    x = rnorm(100, mean = 4, sd = 3)
  )

sim_data |> 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
```

```{r}
sim_mean_sd = function(samp_size, mu = 3, sigma = 4) {
  
  sim_data = 
    tibble(
      x = rnorm(n = samp_size, mean = mu, sd = sigma)
    )

  sim_data |> 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
}

sim_mean_sd(samp_size = 100, mu = 6, sigma = 3)

sim_mean_sd(samp_size = 100)
```



## Let's review Napoleon Dynamite

## Mean scoping example

```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```



## Functions as arguments

```{r}
my_summary = function(x, summ_func) {
  
  summ_func(x)
  
}

x_vec = rnorm(100, 3, 7)

mean(x_vec)
median(x_vec)

my_summary(x_vec, IQR)
```



## Lists

You can put anything in a list.

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat = matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
)
```

```{r}
l
l$vec_numeric
l[(1)]
```

## 'for' loop

```{r}
list_norm = 
  list(
    a = rnorm(20, mean = 3, sd = 1),
    b = rnorm(30, mean = 0, sd = 5),
    c = rnorm(40, mean = 10, sd = .2),
    d = rnorm(20, mean = 3, sd = 1)
  )
```

```{r}
list_norm
```

Pause and get my old function.

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```

I can apply that function to each list element.

```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
```

Let's use a for loop:

```{r}
output = vector("list", length = 4)

output[[1]] = mean_and_sd(list_norm[[1]])

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
  
}
```



## Let's try map!

```{r}
output = map(list_norm, mean_and_sd)
```

What if you want a different function..?

```{r}
output = map(list_norm, IQR)
```











